Generative Adversarial Networks

### 2017-11-12 cs6735/project/draft.tex
finishe motivation sectin

\begin{abstract}
    General Adversarial Networks have
\end{abstract}

@@

>>>>

\begin{abstract}
    Deep generative networks have often fallen short, especial when compared to discriminative models. Since their conception in 2014, generative adversarial networks have seen exponential growth in research. These networks offer promising results for both unsupervised learning and generative models. This research paper presents an overview of generative adversarial networks. Specifically, we will examine the motivation behind GANs, their theoretical justification, the current state of GANs and the research frontiers that have yet to be explored.
\end{abstract}

@@

\section{Motivations}
There exists several compelling reasons for studying generative modeling \citep{2017arXiv170100160G}. These models are extremely useful when your goal is understand the underlying distribution parameters. For example, joint probability distributions of high dimensional data is relevant to both applied math and engineering \citep{2017arXiv170100160G}. Generative models are also applicable to reinforcement learning, particularly model-based learning algorithms. A time series generative model, one which predicts future states of an environment given the current state of the environment and an agents actions, are of particular interest \citep{2017arXiv170100160G}. An agent may learn the best action to take in a given scenario by querying this generative model and choosing the one which outputs the best state of the world. Furthermore, generative models, especially GANs, have recently excelled at semi-supervised learning.

Proposed in the original GAN paper \citep{2014arXiv1406.2661G}, semi-supervised techniques used in conjunction with GANs have recently proven themselves as a reputable technique. The premise involves training the discriminator to classify images into $n + 1$ classes where $n$ is the number of class labels and the additional $1$ is the class of a fake image. This algorithm is able to obtain great performance on relatively small labeled datasets when compared to labeled datasets typically state of the art supervised algorithms \citep{2017arXiv170100160G}. Currently, the best performing semi-supervised GAN are feature matching GANs, where the new objective of the generative model is to minimize the distance between a layer $l$ of the discriminator \citep{2016arXiv160603498S}.

Many applications require multi-modal outputs. For example, predicting the next action of a self-driving car. Within this context, it is important the model not be trained by traditional methods, such as using mean squared error to minimize the distance between the expected and predicted actions. These models cannot be used in situations where there is more than one appropriate prediction. Generative modeling, especially GAN, allow machine learning to function the scenarios where one input corresponds to multiple acceptable outputs \citep{2017arXiv170100160G}.

Tasks which involve image generation, modification or translation are all highly applicable to generative models. Although GANs may be used to generate any type of data, images remain the most commonly used source of training data. Research conducted within the past three years demonstrates the capabilities of GANs to perform these tasks \citep{2017arXiv170100160G, 2016arXiv161102200T, 2014arXiv1411.1784M}. For example, GANs have recently been shown to be capable of translating aerial photographs into maps and sketches into realistic images \citep{2017arXiv170100160G}.
